\LARGE \bf A Pipeline to Assemble (Near-)Collision Footage Datasets

### 2021-03-27 paper.tex
added batch size
changed wording

In order to evaluate the importance of acquiring data from multiple geographical locations and under varying driving conditions around the world, we have manually collected a dataset of 223 video clips on which we will test the existing collision anticipation model, DSARNN.  This dataset is comprised of 97 positive and 126 negative videos. Most of these videos represent road scenes from North America, Europe and Russia which have noticeably different characteristics than those in Taiwan. To prepare our data we follow the steps outlined by Chan et. al \cite{chan2016anticipating}. Namely, we trim videos such that they are 5 seconds long sampled at 20fps. We trim such that the collision occurs at frame 90, i.e. the first 90 frames are used for collision prediction. This trimming and sampling functionality is provided within a configuration of our pipeline. In our experiments we use the DSARNN model to be trained on features produced by a running a VGG \cite{DBLP:journals/corr/SimonyanZ14a} on each full frame and the cropped objects within the frame and concatenating the output. This is denoted VGG+RNN+F+D-con. in the original publication. We note that this data includes manually annotated bounding boxes, so there will be no error imposed by using automated vehicle detection and localization models.

In our first experiment we merge our dataset with the dataset provided by Chan et. al. We augment their train set with 77 positives and 106 negatives, and their test set with 20 positives and 20 negatives. We use the same training procedure as Chan et. al, namely we train for 40 epochs with a learning rate of $10^{-4}$. Although our data contribution here is relatively small, we observe a mean time-to-accident of 2.198 at 80\% recall which is very similar to the existing results from Chan et. al, however we observe an average precision of 66.22\% which is appreciably lower than the 73.53\% average precision reported by Chan et. al.

>>>>

In order to evaluate the importance of acquiring data from multiple geographical locations and under varying driving conditions around the world, we have manually collected a dataset of 223 video clips on which we will test the existing collision anticipation model, DSARNN.  This dataset is comprised of 97 positive and 126 negative videos. Most of these videos represent road scenes from North America, Europe and Russia which have noticeably different characteristics than those in Taiwan. To prepare our data we follow the steps outlined by Chan et. al \cite{chan2016anticipating}. Namely, we trim videos such that they are 5 seconds long sampled at 20fps and the collision occurs at frame 90. This trimming and sampling functionality is provided within a configuration of our pipeline. In our experiments we use the DSARNN model to be trained on features produced by a running a VGG \cite{DBLP:journals/corr/SimonyanZ14a} on each full frame and the cropped objects within the frame and concatenating the output. This is denoted VGG+RNN+F+D-con. in the original publication. We note that this data includes manually annotated bounding boxes, so there will be no error imposed by using automated vehicle detection and localization models.

In our first experiment we merge our dataset with the dataset provided by Chan et. al. We augment their train set with 77 positives and 106 negatives, and their test set with 20 positives and 20 negatives. We use the same training procedure as Chan et. al, namely we train for 40 epochs with a learning rate of $10^{-4}$ and a batch size of 10. Although our data contribution here is relatively small, we observe a mean time-to-accident of 2.198 at 80\% recall which is very similar to the existing results from Chan et. al, however we observe an average precision of 66.22\% which is appreciably lower than the 73.53\% average precision reported by Chan et. al.
